\vspace{60pt}\\ \huge \bfseries Skedge \\ \vspace{10pt} \Large Smarter course scheduling for our University

### 2016-04-13 analytics/npa.tex
little updates

    \caption{Frequency of navigations-per-adds when the goal was to \emph{add a specific course}}
    \label{fig:navs-direct}
  \end{figure}

@@

    \caption{Frequency of navigations-per-add/bookmark when the goal was to \emph{browse for courses}}
    \label{fig:navs-browse}
  \end{figure}

@@

  :(

>>>>

    \caption{Frequency of navigations-per-adds for the goal of \emph{adding a specific course}}
    \label{fig:navs-direct}
  \end{figure}

@@

    \caption{Frequency of navigations-per-add/bookmark for the goal of \emph{browsing for courses}}
    \label{fig:navs-browse}
  \end{figure}

@@

  Given more time with Skedge Social being live and more forethought in tracking its usage, similar data analysis could be done on the subject of the effectiveness of Skedge in peer-guided course finding. Unfortunately, usage data to answer questions such as ``how many Facebook friends were listed as liking or taking a course when it was added?'', and cannot be retroactively computed due to Skedge's purposeful privacy limitations (Facebook friend data can only be retrieved client-side---no data is stored on the server that could authorize such a data request). Thus, part (c) of hypothesis \#2 cannot be verified.

### 2016-04-13 analytics/usage.tex
little updates

In this section, I will address many of the features listed in Chapter 2 (Design) and demonstrate their usability. To date, Skedge has seen\ldots

\begin{center}
\begin{tabular}{l}
  \hline
  4,713 users that have added or bookmarked at least one course \\ 
  5,256 schedules, with an average of 5.13 and median of 5 sections per schedule \\ 
  75\% of sessions from returning visitors \\ 
  107 sessions averaged per day \\ 
  5.4 pages viewed averaged per session  \\ 
  6 minutes spent averaged per session \\ 
  \hline
\end{tabular}
\end{center}

@@

  \caption{Searches over the period Oct 19 2015 to Apr 11 2016, annotated with major events}
  \label{fig:searches}

@@

{\renewcommand{\arraystretch}{1.5}
\singlespacing
\begin{center}
\begin{tabular}{l}
  \hline
  141 users have linked Skedge to Facebook \\
  10,242 page views (256 page views/day)  \\
  10 pages/session (users cycle through tabs and go back to it) \\
  a 5\% bounce rate (users interact with it) \\
  67\% of visits being were returning visitors \\
  284 overlays onto friends’ schedules (2 per user) \\
  \hline
\end{tabular}
\end{center}
\doublespacing

@@

\noindent Although the feature is too young for in-depth data analysis, these initial reports show promise, especially in the rate of adoption (around 3.5 users per day on average), its level of interaction, and the rate of \emph{returning} users to Skedge Social.

@@

  \caption{Hovering over a course block in Skedge's side-schedule shows at-a-glance information about it; clicking on it navigates the user to that course}
  \label{fig:searchtypes}

>>>>

In this section, I will adress the usability of the features listed in Chapter 2 (Design). But first, here are some general statistics of Skedge to date:

\vspace{7pt}

\onehalfspacing
\begin{center}
\begin{tabular}{l}
  \hline
  4,713 users that have added or bookmarked at least one course \\ 
  5,256 schedules, with an average of 5.13 and median of 5 sections per schedule \\ 
  75\% of sessions from returning visitors \\ 
  107 sessions averaged per day \\ 
  5.4 pages viewed averaged per session  \\ 
  6 minutes spent averaged per session \\ 
  \hline
\end{tabular}
\end{center}
\doublespacing

@@

  \caption[Searches over the period Oct 19 2015 to Apr 11 2016]{Searches over the period Oct 19 2015 to Apr 11 2016, annotated with major events}
  \label{fig:searches}

@@

{\renewcommand{\arraystretch}{1.5}
\singlespacing
\begin{center}
\begin{tabular}{l}
  \hline
  141 users have linked Skedge to Facebook ($\sim$3.5 per day) \\
  10,242 page views (256 page views/day)  \\
  10 pages/session (users cycle through its tabs and repeatedly return to it) \\
  a 5\% bounce rate (users interact with the page before leaving) \\
  67\% of visits being were returning visitors \\
  284 overlays onto friends’ schedules (2 per user) \\
  \hline
\end{tabular}
\end{center}
\doublespacing

@@

\noindent Although the feature is too young for in-depth data analysis, these initial reports show promise, especially in the rate of adoption, its level of interaction, and the rate of returning users to Skedge Social.

@@

  \caption[Course blocks in Skedge]{Hovering over a course block in Skedge's side-schedule shows at-a-glance information about it; clicking on it navigates the user to that course}
  \label{fig:searchtypes}

### 2016-04-13 design/social.tex
little updates

  \begin{figure}[H]
      \centering
      \fbox{
        \includegraphics[width=9cm]{images/skedge/social-login}
      }
      \caption{Skedge Social landing page (\url{http://skedgeur.com/social}) for a user whose account has not yet been integrated with Facebook. Skedge Social appears in the context of the ordinary Skedge interface, and is accessible with the globe icon to the right of the searchbar.} \label{fig:sk-social-login}
    \end{figure}

@@

    \begin{figure}
      \centering
      \fbox{
        \includegraphics[width=9cm]{images/skedge/social}
      }
      \caption{Skedge Social's schedule feed (the default of four tabs) for a user who has integrated their Skedge account with Facebook. The user can toggle between a peer's schedule and the list of their \emph{liked} courses.} \label{fig:sk-feed}
    \end{figure}

@@

      \begin{subfigure}[w]{6.5cm}
        \centering
        \includegraphics[height=1.5cm]{images/skedge/social-note2}
        \caption{\emph{New friends} notification} \label{fig:sk-social-note2}
      \end{subfigure}
    \end{tabular}
    \caption{Notifications: none, one, or both of them can adorn the Skedge Social logo}
  \end{figure}

>>>>

  \begin{figure}[H]
      \centering
      \fbox{
        \includegraphics[width=9cm]{images/skedge/social-login}
      }
      \caption[Skedge Social landing page for a user who hasn't yet joined it]{Skedge Social landing page (\url{http://skedgeur.com/social}) for a user who hasn't yet joined it. Skedge Social appears in the context of the ordinary Skedge interface, and is accessible with the globe icon to the right of the searchbar.} \label{fig:sk-social-login}
    \end{figure}

@@

    \begin{figure}
      \centering
      \fbox{
        \includegraphics[width=9cm]{images/skedge/social}
      }
      \caption[Skedge Social's schedule feed]{Skedge Social's schedule feed (the default of four tabs) for a user who has integrated their Skedge account with Facebook. The user can toggle between a peer's schedule and the list of their \emph{liked} courses.} \label{fig:sk-feed}
    \end{figure}

@@

      \begin{subfigure}[w]{6.5cm}
        \centering
        \includegraphics[height=1.5cm]{images/skedge/social-note2}
        \caption{\emph{New friends} notification} \label{fig:sk-social-note2}
      \end{subfigure}
    \end{tabular}
    \caption[Skedge Social's notifications]{Notifications: none, one, or both of them can adorn the Skedge Social logo}
  \end{figure}

### 2016-04-13 paper.tex
little updates

\title{
\vspace{50pt}\\
\huge \bfseries SKEDGE
\\
\vspace{10pt}
\Large
Smarter course scheduling for our\\
University of Rochester
}

@@

\date{April 13, 2016\\
    \vspace{100pt}\\
    submitted in partial fulfillment of\\
    the requirements for the degree\\
    \emph{honors bachelor of science}\\
    \vspace{30pt}\\
    and as an open letter addressed to\\
    the information technology staff\\
    at the university of rochester
    \vspace{-30pt}
}

>>>>

\title{
\vspace{60pt}\\
\huge \bfseries Skedge \\
\vspace{10pt}
\Large
Smarter course scheduling for our University
}

@@

\date{April 13, 2016\\
    \vspace{80pt}\\
    submitted in partial fulfillment of\\
    the requirements for the degree\\
    \emph{honors bachelor of science},\\
    \vspace{40pt}\\
    and as an open letter addressed to\\
    the information technology staff\\
    at the university of rochester
    \vspace{-80pt}
}
